upwell_IDX

### 2019-08-21 upwell_IDX.Rmd
update

Increase in upwelling over the past years as a result of intensified winds over time?
Weakening of th upwelling over time, leads to a decrease in the upwelling indexs
Strong south easterly winds - Spring and summer: Upwelling is more intense in spring and summer months
The formula used suggests that if values at + upwelling occurs and if values are - then downwelling occurs. But the intensity of upwelling changes.
Compare upwelling indeces per season

@@

# Wind speed intensifed ovwer the years
Take first third (33percentile) of the data and the last third (66th percentile) of the data for every season and then do a t-test

>>>>

##### Upwelling #####
# Min duration for an upwelling event - 1day and threshold -1. Upwelling can over within a few hours, but given that we have daily data - upwelling has a minimum duration of 1 day
# Seasonal upwelling. Upwelling seasons are summer and spring
# Did the wind intensify? This is usually done by taking first third of the dataset and the last thid of the dataset and doing a t-test on this
# Strong south easterly winds lead to a stronger upwelling event

@@

# Wind speed intensifed over the years
Take first third (33percentile) of the data and the last third (66th percentile) of the data for every season and then do a t-test
